Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-04-17 README.Rmd
updated readme
preparing preprint

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), 
R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428),
Jacob Freeman [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7402-8450), 
Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), 
Robert L. Kelly[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9737-0152), 
(2020). _`r Title`_. Under review.

<!-- Our pre-print is online here: -->

<!-- > Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

@@

> Bocinsky, R. Kyle and Erick Robinson, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@

The **analysis** directory contains:

@@

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip). After unzipping, open the `Proj` file in RStudio, and run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). Then open `paper.Rmd` and knit to produce the `paper.docx`.

>>>>

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), 
R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428),
Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), 
Jacob Freeman [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7402-8450), 
Robert L. Kelly[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9737-0152), 
(2020). _`r Title`_. *Philosophical Transactions B*. In Press.

@@

> Bocinsky, R. Kyle, Darcy Bird, and Erick Robinson, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@

The [:file_folder: analysis](/analysis) directory contains:

@@

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip). After unzipping, open the `Proj` file in RStudio, and run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). Then open `robinson2020.Rmd` and knit to produce the paper in PDF format.
